### 2016-05-16 text/ms.Rmd
Copy editing and cleaning

In fisheries science, the commonly used operational models for determining
status and trend of exploited fish populations are stock assessments, i.e.,
population models coupled to an observation model, that incorporate all
appropriate data (e.g. catches, size and age distributions, surveys, and
tagging information) to quantify values such as the biomass of a stock that
can produce maximum sustainable yield ($B_\mathrm{MSY}$) [@hilborn1992].
However, the broad range of data required to conduct these stock assessments
are not available for the majority of fish populations, including those of
conservation concern and of economic interest to fisheries [@fao2014].
Therefore, a number of models have been proposed to assess $B/B_\mathrm{MSY}$
based on the limited data available for the majority of fish stocks: (1) a time
series of the total biomass of catch and (2) a basic understanding of
population productivity [e.g. @vasconcellos2005; @martell2013]. Recently,
@rosenberg2014 investigated the performance of four data-limited models through
a large-scale simulation experiment. Three of these models were based on
Schaefer (logistic) biomass dynamics and one was an empirical model fitted to
more data-rich stock-assessment output. The four models frequently disagreed
about population status (e.g. Fig. \ref{motivate}), no one model had strong
performance across all fish stocks, and some models performed better than
others depending on circumstances.

Here, we estimate population status and trend of exploited fish populations
using ensembles and superensembles (collectively 'ensemble methods') of these
four data-limited models. We apply four ensemble-method approaches of varying
complexity to both simulated and real-world fish stocks and compare their
predictive performance against each other and the individual models.

@@

<!--TODO Add in the reference to (Fig. \ref{didactic}) and reorder the figures and add
in the figure with the partial dependence -->

@@

We used the mean or slope of $B/B_\mathrm{MSY}$ as the response variable and
the predictions from the individual models as predictors in our superensemble
models. When modelling mean $B/B_\mathrm{MSY}$ --- a ratio bounded at zero ---
we fit the superensemble models in log space and exponentiated the
predictions. For the estimates of $B/B_\mathrm{MSY}$ slope, which are not
bounded at zero, we fit superensemble models on the natural untransformed
scale.

TODO: standardize notation of the following with figure 2

We compared an ensemble average and three superensembles of varying
complexity: a linear model with two-way interactions, a random forest, and a
boosted regression tree. We describe these models as estimating
$\hat{\theta}$, which represents either the ensemble estimated $\log
B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$. The individual model
estimates of $\log B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$ are
represented as $\hat{b}$ for models $i$ $1$ through $4$ (CMSY, SSCOM, COM-SIR, mPRM).
The ensemble average for each fishery $i$ was calculated as:

@@

Once the superensemble models are built, we can apply them to new stocks that
we'd like to know the status of. To do this we applied the individual models
to our stocks of interest and then applied these data to our already built
superensemble models. In this paper we applied the superensemble models to
subsets of the simulated data as a cross-validation test and to the RAM Legacy
Stock Assessment database to test on real stocks.

@@

<!-- Dan: Lastly, it's worth noting that this approach, as laid out here is for
helping improve potentially conflicting estimates of the same metric, B/Bmsy. In
many cases though a fishery is going to be basing its decisions on streams of
multiple indicators, e.g trends in SPR and B/Bmsy. While the ensemble methods
here can help refine estimates of individual metrics, it's still worth looking
at what alternative data streams are telling you if possible. E.g. if a purely
catch based B/Bmsy estimate is high and has a positive slope, but mean lengths
and SPR are decreasing, managers will still need to think about how to deal with
these conflicting signals. So, this ensemble method, as I interpret it, is
helpful for resolving conflicts within metric, but doesn't necesarily resolve
conflicts across metrics (if I'm understanding these methods right) -->

@@

<!-- TODO put back when space: or to evaluate the effect of conservation
management actions when experimental or observational data are limited
[@walsh2012].-->

@@

<!--Funding...-->

<!--# Citation notes-->

<!--
- @breiner2015 ensemble models of species distribution models for rare species

- @jones2015 ensemble models of species distribution models - globally for
  marine biodiversity

- [@greene2006] example similar to ours but with climate models (Bayesian
  multilevel ensemble)

- [@kell2007] FLR

- multiple learners book [@alpaydin2010]

- [@caruana2004] nice paper on ensemble models; prob of overfitting increases
  with more models, bagging important

- [@tebaldi2007] key paper: review of 'multi-model ensembles for climate projections'

- famous ensemble is DEMETER: Development of a European Multi-model Ensemble
  System for Seasonal to Interannual Prediction @hagedorn2005 is a good
  reference

- Examples of where ensemble models are shown to be better than any one:
  @thomson2006 (public health - malaria), @cantelaube2005 (agriculture - crop
  yield) (citations taken from @tebaldi2007)

- simple averages are used very commonly in climate science - e.g. IPCC 2001

- @tebaldi2007: weighting obviously makes sense, but how do we define a
  performance metric that is based on past observations that is relevant to the
  future?

- @tebaldi2007: model independence important

- for climate, weighted averages perform better than simple averages [@min2006],
  but are those same weights applicable to the future (or in our case other
  fisheries)?

Why do ensemble methods work?

- error cancellation is one but not the only reason for superiority of ensemble
  models [@hagedorn2005]

- ensemble model may be only marginally better than the best single model in
  any given case, but we don't usually know which is the best single model
  [@hagedorn2005]

- ensemble models useful for regional climate models too; as an example,
  @pierce2009 use 42 metrics to characterize model performance in regional
  climate model ensembles; found that ensemble models were superior to any one
  model --- especially when considering multiple metrics

- @knutti2009: key review paper on motivation and challenges of combining
  climate projection models; performance on testing / current data may only
  weakly relate to future / other datasets

- @murphy2004: Nature paper on ensembles of climate model simulations; weighted
  average better performance than unweighted average

- @dietterich2000: highly cited book chapter "Ensemble Methods in Machine
  Learning"; ensembles are often much more accurate than the "individual
  classifiers that make them up"; but components must be diverse and accurate

- @dietterich2000: a main justification for ensembles: they are
  representational --- no one model usually can contain all hypothetical
  functional forms, but many separate models can cover more hypotheses

- strong paper showing that ensemble models are most accurate when the various
  individual models make errors in uncorrelated ways [@ali1996]

- without substantial training-testing data, appropriate model weights can be
  very hard to deduce and can cause more harm than good (compared to equal
  weighting) [@weigel2010] (they give the example of seasonal forecasting where
  a ton of hind cast testing can be done, vs. long-term climate) (asymmetrical
  loss function)

- [@weigel2010] optimal weights are always as good or better than equal
  weights, but if you get the weights wrong, you can be better off just using
  equal weights; but averaging was almost always better than any one model

- @rykiel1996 "Testing ecological models: the meaning of validation" (see for
  performance criteria, theory on model testing and assessment)

model averaging AIC:
f Chamberlin 1890).  multiple woring hypotheses
  (e.g., Johnson and Omland 2004, Hobbs and Hilborn 2006, Burnham et al. 2011,
  52 Grueber et al. 2011).
-->

<!-- vim: set formatoptions=nroq: -->

>>>>

In fisheries science, the commonly used operational models for determining
status and trend of exploited fish populations are stock assessments, i.e.,
population models coupled to an observation model that incorporate all
appropriate data (e.g. catches, size and age distributions, surveys, and
tagging information) to quantify values such as the biomass of a stock that
can produce maximum sustainable yield ($B_\mathrm{MSY}$) [@hilborn1992].
However, the broad range of data required to conduct these stock assessments
are not available for the majority of fish populations, including those of
conservation concern and of economic interest to fisheries [@fao2014].
Therefore, a number of models have been proposed to assess $B/B_\mathrm{MSY}$
based on the limited data available for the majority of fish stocks: (1) a time
series of the total biomass of catch and (2) a basic understanding of
population productivity [e.g. @vasconcellos2005; @martell2013]. Recently,
@rosenberg2014 investigated the performance of four data-limited models through
a large-scale simulation experiment. Three of these models were based on
Schaefer (logistic) biomass dynamics and one was an empirical model fitted to
more data-rich stock-assessment output. The four models frequently disagreed
about population status (e.g. Fig. \ref{motivate}), no one model had strong
performance across all fish stocks, and some models performed better than
others depending on circumstances.

Here, we estimate population status and trend of exploited fish populations
using ensembles and superensembles (collectively "ensemble methods") of these
four data-limited models. We apply four ensemble-method approaches of varying
complexity to both simulated and real-world fish stocks and compare their
predictive performance against each other and the individual models.

@@

TODO ADD OVERVIEW HERE.

@@

We used the mean or slope of $B/B_\mathrm{MSY}$ as the response variable and the
predictions from the individual models as predictors in our superensemble models
(Fig. \ref{didactic}a). When modelling mean $B/B_\mathrm{MSY}$ --- a ratio
bounded at zero --- we fit the superensemble models in log space and
exponentiated the predictions. For the estimates of $B/B_\mathrm{MSY}$ slope,
which are not bounded at zero, we fit superensemble models on the natural
untransformed scale.

We compared an ensemble average and three superensembles of varying complexity:
a linear model with two-way interactions, a random forest, and a boosted
regression tree. We describe these models as estimating $\hat{\theta}$, which
represents either the ensemble estimated $\log B/B_\mathrm{MSY}$ or slope of
$B/B_\mathrm{MSY}$. The individual model estimates of $\log B/B_\mathrm{MSY}$ or
slope of $B/B_\mathrm{MSY}$ are represented as $\hat{b}$ for models $i$ $1$
through $4$ (CMSY, COM-SIR, SSCOM, mPRM). The ensemble average for each fishery
$i$ was calculated as:

@@

Once the superensemble models are built, we can apply them to new stocks to
estimate their status (Fig. \ref{didactic}b). To do this we applied the
individual models to our stocks of interest and then applied these data to our
already built superensemble models. In this paper we applied the superensemble
models to subsets of the simulated data as a cross-validation test and to the
RAM Legacy Stock Assessment database to test on real stocks.

@@

@@

@@
